Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-06 paper/main.tex
Updates

\begin{equation}
	\rho_{X, Y} = \frac{\mathrm{cov}(X, Y)}{\sigma_X \sigma_Y}
\end{equation}

@@

\begin{equation}
	\rho_{X, Y; \bm{Z}} = \rho_{R_X, R_Y}
\end{equation}

@@

\begin{equation}
	\rho_{X, Y} = \frac{\Sigma_{XY}}{\sqrt{\Sigma_{XX} \Sigma_{YY}}}
\end{equation}

@@

\begin{equation}
	\rho_{X, Y; \bm{Z}} = - \frac{\Sigma^{-1}_{XY}}{\sqrt{\Sigma^{-1}_{XX} \Sigma^{-1}_{YY}}}
\end{equation}

@@

\begin{definition}
	Given two sets of random variables $ \bm{U} = (U_1, U_2, \cdots, U_p) $
	and $ \bm{V} = (V_1, V_2, \cdots, V_q) $, canonical correlation between
	them, $\upsilon(\bm{U}, \bm{V}) $ is defined as:

@@

Several measures of association have been derived from canonical correlations, such as:
\begin{itemize}
	\item Wilks' Lambda: $\Lambda = \prod_{i}^{\min(p, q)} (1 - \nu_i^2) $
	\item Roy's Largest Root: $ \theta = \max_i(\nu_i^2) $
	\item Pillai's Trace: $ \tau = \sum_{i=1}^{\min(p, q)} \nu_i^2 $
\end{itemize}

@@

\begin{equation}
	\rho(X, Y; \bm{Z}) = \frac{1}{\min(\rvert R_x \rvert, \rvert R_y \rvert)}
	\sum_{i=1}^{\min(\rvert R_x \rvert, \rvert R_y \rvert)} (\nu_i(R_x, R_y))^2
\end{equation}

>>>>

\begin{equation}
	r_{X, Y} = \frac{\mathrm{cov}(X, Y)}{\sigma_X \sigma_Y}
\end{equation}

@@

\begin{equation}
	r_{X, Y; \bm{Z}} = r_{R_X, R_Y}
\end{equation}

@@

\begin{equation}
	r_{X, Y} = \frac{\Sigma_{XY}}{\sqrt{\Sigma_{XX} \Sigma_{YY}}}
\end{equation}

@@

\begin{equation}
	r_{X, Y; \bm{Z}} = - \frac{\Sigma^{-1}_{XY}}{\sqrt{\Sigma^{-1}_{XX} \Sigma^{-1}_{YY}}}
\end{equation}

@@

\begin{definition}
	Given two sets of random variables $ \bm{U} = (U_1, U_2, \cdots, U_p) $
	and $ \bm{V} = (V_1, V_2, \cdots, V_q) $, canonical correlation between
	them, $\rho_{\bm{U}, \bm{V}} $ is defined as:

@@

Several measures of association have been derived from canonical correlations, such as:
\begin{itemize}
	\item Wilks' Lambda: $\Lambda = \prod_{i}^{\min(p, q)} (1 - \rho_i^2) $
	\item Roy's Largest Root: $ \theta = \max_i(\rho_i^2) $
	\item Pillai's Trace: $ \tau = \sum_{i=1}^{\min(p, q)} \rho_i^2 $
\end{itemize}

@@

\begin{equation}
	\tau_{X, Y; \bm{Z}} = \frac{1}{\min(\rvert R_x \rvert, \rvert R_y \rvert)}
	\sum_{i=1}^{\min(\rvert R_x \rvert, \rvert R_y \rvert)} (\rho_{R_x, R_y})_i^2
\end{equation}
